---
title: "MATH 3070 Lab Project 6"
author: "Kyle Kazemini"
date: "September 26, 2019"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1
*For the `UScereal` (**MASS**) data set, create a scatter plot of `calories` modeled by `sugars` using the `shelf` variable to create different plot characters. Add a legend to indicate the shelf number. Is there any patterns? (Use base R plotting for this problem.)*

```{r, tidy=TRUE, error=TRUE}
library(MASS)
data("UScereal")
str(UScereal) #Displays Structure 
plot(UScereal$sugars, UScereal$calories,
main = "Sugars vs Calories", xlab = "Sugars",
ylab = "Calories", pch = as.numeric(UScereal$shelf),) 
#Creates plot with the specified parameters
#The plot uses the shelf variable to create plot characters
legend(18,450,c("1","2","3"),col = 1:3, pch = 1:3)
#Creates a legend for our plot with the specified coordinates
```

## Problem 2
*For the data set `UScereal` (**MASS**) make a pairs plot of the numeric variables. Which correlation looks larger: fat and calories or fat and sugars?*

```{r, tidy=TRUE, error=TRUE}
pairs(UScereal[c("calories","protein","fat","sodium","fibre","carbo","sugars","shelf","potassium")])
#The correlation between calories and fat looks larger because the values are more tightly packed 
# (excluding a couple of outliers)
```

## Problem 3
*For the data set `batting` (**UsingR**) make a bubble plot of home runs hit (`HR`) modeled by hits (`H`) where the scale factor for each point is given by `sqrt(SO)/10`. Is there any story to be told by the size of the points? (You must use base R plotting for this problem.)*

```{r, tidy=TRUE, error=TRUE}
library(UsingR)
data("batting")
plot(batting$H, batting$HR, xlab = "H", ylab = "HR", main = "H vs HR",
     pch = 16, col=rgb(red = 0, green = 0, blue = 0, alpha = 0.250),
     cex = sqrt(batting$SO/10))
#Creates bubble plot with specified parameters and scale factor
#The size of the point is proportional to the number of strike outs. Batters with a lot of hits 
# also have a lot of strikeouts
```

