---
title: "MATH 3070 Lab Project 2"
author: "Kyle Kazemini"
date: "08/29/2019"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1
*The `exec.pay` (**UsingR**) data set is available after loading the package **UsingR**. Load the package, and inspect the data set. Scan the values to find the largest one.*

```{r}
library(UsingR) #loads library
data("exec.pay") #loads data set
max(exec.pay, na.rm=TRUE) #finds max value in data set
```

## Problem 2
*Create the following sequences, using `:`, `seq()`, or `rep()` as appropriate:*

1. `"a" "a" "a" "a" "a" `

```{r}
rep("a",times=5) #repeat "a" 5 times
```

2. `1 3 ... 99` *(the odd numbers)*

```{r}
seq(1,99,2) #sequence from 1 to 99 skipping evens
```

3. `1 1 1 2 2 2 3 3 3`

```{r}
rep(c(1, 2, 3), each=3) #repeats the numbers three times each
```

## Problem 3
*Let our small data set be* `2 5 4 10 8`.

1. *Enter this data into a data vector `x`.*

```{r}
x <- c(2,5,4,10,8) #vector x with values of the data set
```

2. *Find the square of each number.*

```{r}
x2 <- x^2 #sets x2 to x^2
x2 #displays result
```

3. *Subtract 6 from each number.*

```{r}
x3 <- x-6 #subtracts 6
x3 #displays result
```

4. *Subtract 9 from each number and then square the answer.*

```{r}
x4 <- (x-9)^2 #makes calculation
x4 #displays result
```