---
title: "MATH 3070 Lab Project 4"
author: "Kyle Kazemini"
date: "09/12/2019"
output:
  html_document:
    toc: TRUE
---
4
*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 
*The `time` variable in the `nym.2002` data set (**UsingR**) contains the time to finish the 2002 New York City Marathon for a random sample of the finishers.*

1. *What percent ran the race in under 3 hours?*

```{r}
library(UsingR)
data(nym.2002)
str(nym.2002) #structure of data
which(nym.2002$time<180) #displays which positions have a value less than 180
length(which(nym.2002$time<180))/length(nym.2002$time) #finds the percentage of values less than 180
```

2. *Given that the slower runners will have higher running times; cut off the highest 10%.The highest 25%*

```{r}
quantile(nym.2002$time,0.9) #displays bottom 90% of the data
quantile(nym.2002$time,0.75) #displays bottom 75% of the data
```

3. *Given that the faster runners will have lower running times, cut off the lowest 10%.*

```{r}
quantile(nym.2002$time,0.1) #displays cutoff for lowest 10%
```

## Problem 2 
*The data set `UScereal` (**MASS**) contains data on cereals sold in the United States in 1993. For this data set, answer the following questions using R (i.e. MUST answer questions using a code. Do not count by hand):*

1. *How many rows does the data frame have? Columns?*

```{r}
library(UsingR)
data("UScereal")
nrow(UScereal) #displays number of rows
ncol(UScereal) #displays number of columns
```

2. *How many different manufacturers are included?*

```{r}
length(UScereal$mfr) #displays number of manufacturers in data set
```

3. *How many vitamin categories are included?*

```{r}
levels(UScereal$vitamins) #displays categories
length(levels(UScereal$vitamins)) #displays number of categories
```

4. *How many cereals have a sugar level above 10?*

```{r}
which(UScereal$sugars>10) #displays how many cereals have greater than 10 grams of sugar
length(which(UScereal$sugars>10)) #displays length of cereals with greater than 10 grams of sugar
```

5. *What is the mean calorie value for cereals with more than 5 grams of fat? Less than or equal to 5?*

```{r}
mean(which(UScereal$fat>5)) #displays mean of cereals with more than 5 grams of fat
length(mean(which(UScereal$fat>5))) #displays length
mean(which(UScereal$fat<=5)) #displays mean of cereals with less than or equal to 5 grams of fat
length(mean(which(UScereal$fat<=5))) #displays length
```

6. *What is the mean calorie value for cereals on the middle shelf (2)?*

```{r}
mean(which(UScereal$shelf==2)) #displays mean calorie value for middle shelf cereals
```

## Problem 3
*Create a data frame containing the data in the following table:*

| First    | Last      | Age |
|----------|-----------|-----|
| Marcus   | Holstein  | 23  |
| Samuel   | Adams     | 56  |
| Gus      | McPherson | 43  |
| Margaret | Olsen     | 41  |
| Zim      | Newbold   | 95  |

```{r}
df <- data.frame("First" = c("Marcus","Samuel","Gus","Margaret","Zim"), 
"Last" = c("Holstein", "Adams", "McPherson", "Olsen", "Newbold"),"Age" =c(23,56,43,41,95))
#creates data set with Specified columns and entries
```
