---
title: "MATH 3070 Lab Project 8"
author: "Kyle Kazemini"
date: "October 17, 2019"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1
*For the `michelson` (**MASS**) data set, produce a density plot comparing `Speed` between Experiments 1 and 2.*

```{r, tidy=TRUE, error=TRUE}
library(MASS)
data("michelson")
str(michelson)
Speed_split <- with(michelson, split(Speed, Expt)) #Creates a list with the variables we want
Expt1 <- Speed_split$`1` #For experiment 1
Expt2 <- Speed_split$`2` #For experiment 2
plot(density(Expt1), lty = 1) #Creates density plot of the two lines
lines(density(Expt2), lty = 2)
```

## Problem 2
*Three students record the time spent on homework per class. Their data is:*

| Student| 1  | 2  | 3  | 4  | 5 |
|:-------|---:|---:|---:|---:|--:|
| Marsha | 25 | 0  | 45 | 90 | 0 |
| Bill   | 30 | 30 | 30 | 30 |   |
| Holly  | 15 | 0  | 90 | 0  |   |

*Use a list to store these values. Then create a boxplot to compare.*

```{r, tidy=TRUE, error=TRUE}
list.student <- list(Marsha = c(25,0,45,90,0), Bill = c(30,30,30,30), Holly = c(15,0,90,0))
#Creates a list with three names and the specified values for each
list.student #Displays list
boxplot(list.student) #Creates boxplot for list
```

## Problem 3
*A group of nursing students take turns measuring some basic assessments. Their data is:*

|          | Temp | Pulse | Systolic | Diastolic |
|----------|------|-------|----------|-----------|
| Jackie   | 98.2 | 96    |  134     | 90        |
| Florence | 98.6 | 56    |  120     | 80        |
| Mildred  | 98.2 | 76    |  150     | 95        |

*Create a data frame of these values. Will `plot()` and `boxplot()` produce the same graphic?*

```{r, tidy=TRUE, error=TRUE}
df <- data.frame(Temp = c(98.2,98.6,98.2), Pulse = c(96,56,76), Systolic = c(134,120,150), Diastolic = c(90,80,95))
#Creates data frame with the given columns
rownames(df) <- c("Jackie","Florence", "Mildred") #Names the rows of the dataframe
df #Displays dataframe
plot(df) #Creates plot
boxplot(df) #Creates boxplot
#Plot and boxplot produce different graphics because of the structure and continuity in the data
```

## Problem 4
*The second argument to `split` can be a list of factors. The result is that all interactions (possible combinations) are used for the groups. In the `ToothGrowth` data set, growth (`len`) is measured for two types of supplements (`supp`) and three doses (`dose`). Split this `len` value into 6 groups.*

```{r, tidy=TRUE, error=TRUE}
data("ToothGrowth")
l1 <- split(ToothGrowth$len, list(ToothGrowth$dose, ToothGrowth$supp)) #Splits len into 6 groups
l1 #Displays l1
```