---
title: "MATH 3070 Lab Project 1"
author: "Kyle Kazemini"
date: "August 23, 2018"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1
*Use R as you would a calculator to find numeric answers to the following:*

1. $-1 + 2(3 + 4)$

```{r}
# simple computation
-1 + 2*(3+4)

```

2. $4^3 + 2^{2 + 3}$

```{r}
# simple computation
4^3 +2^(2+3)

```


## Problem 2
*Use R to compute the following:*
$$\frac{0.25 - 0.2}{\sqrt{0.2(1-0.2)/100}}$$

```{r}
# simple computation
(0.25-0.2)/sqrt(0.2*(1-0.2)/100)
```

## Problem 3
*Assign the numbers 1 through 6 to different variables, then use the variables to multiply all the values.*

```{r}
# initializing variables
var1 = 1
var2 = 2
var3 = 3
var4 = 4
var5 = 5
var6 = 6

# calculating var6 factorial
var1*var2*var3*var4*var5*var6
```

