---
title: "MATH 3070 Lab Project 13"
author: "Kyle Kazemini"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1
*The data set `normtemp` (**UsingR**) contains measurements of 130 healthy, randomly selected individuals. The variable `temperature` contains normal body temperature. Does the data appear to come from a Normal distribution? If so, perform a $t$-test to see if the commonly assumed value of 98.6 degrees fahrenheit is correct. (Studies have suggested that 98.2 degrees fahrenheit is more accurate.)*

```{r, tidy = TRUE}
library(UsingR)
data("normtemp")
str(normtemp)
#Data appears normally distributed, so it's okay to use t.test
t.test(normtemp$temperature, mu = 98.6)
#This t.test shows that for this data, 98.2 is more accurate than 98.6 (with 95 percent confidence)
```

## Problem 2
*In the United States in 2007, the proportion of adults age 21-24 who had no medical insurance was 28.1 percent. A survey of 75 recent college graduates in this age range finds that 40 percent are without insurance. Does this support a difference from the nationwide proportion? Perform a test of significance and report the p-value. Is it significant? (Perform this test "by hand", not using `prop.test()`.)*

```{r, tidy = TRUE}
#Values needed to calculate z
p_hat <- 0.4
n <- 75
p_0 <- .281
#Calculate and display z
z <- (p_hat - p_0)/(sqrt((p_0*(1-p_0))/n))
z
#Use z to find the p value
pval <- 2 * (1 - pnorm(abs(z)))
#Display the p value
pval
```

## Problem 3
*A one-sided, one-sample $t$-test will be performed. What sample size is needed to have a power of 0.80 for a significance level of 0.05 if `delta = 0.05` and the population standard deviation is assumed to be 5?*

```{r, tidy = TRUE}
power.t.test(power = 0.8, delta = 0.05, sd = 5, sig.level = 0.05, type = "paired", 
    alternative = "one.sided")
#This power.t.test finds the value for n for a power value of 0.8
#The other numbers used are given in the question
#n = 61826.93
```

## Problem 4
*For the `babies` (**UsingR**) data set, the variable `age` contains the recorded mom's age and `dage` contains the dad's age for several cases in the sample. Do a significance test of the null hypothesis of equal ages against a one-sided alternative that the dads are older in the sampled population.*

```{r, tidy = TRUE}
library(UsingR)
data("babies")
#Store mom and dad age into variables
mom <- babies$age
dad <- babies$dage
#Use t.test for the significance test
#alternative is less because mom is first, and paired is true because the two are not independent
t.test(mom, dad, paired = TRUE, alternative = "less")
```