---
title: "MATH 3070 Lab Project 7"
author: "Kyle Kazemini"
date: "October 3, 2019"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1
*For the `batting` (**UsingR**) data set, make parallel boxplots of the batting average (`H/AB`) for each team. Which team had the greatest median average? (Use **lattice** functions for this problem.)*

```{r, tidy=TRUE, error=TRUE}
library(UsingR)
data("batting")
str(batting) #Displays structure
library(lattice) #Loads library
bwplot(teamID ~ H/AB, data= batting) #creates lattice plot for each team
#The team with the greatest median average is ANA
```

## Problem 2
*For the `mtcars` data set, produce graphics of the following using **ggplot2**:*

1. *Boxplots for miles per gallon (`mpg`) for groups defined by the number of gears (`gear`).*

```{r, tidy=TRUE, error=TRUE}
data("mtcars")
str(mtcars)
library(ggplot2)
q <- ggplot(mtcars, aes(y= mpg, x= gear, group = gear)) + #Creates plots for each gear
  xlab("Gear") +
  ylab("MPG") + #Names
  ggtitle("Number of gears vs MPG")
q + geom_boxplot() #Creates boxplots
```

3. *A scatterplot of `mpg` modeled by horsepower (`hp`). Create facets by the number of cylinders (`cyl`) and `gear`.*

```{r, tidy=TRUE, error=TRUE}
str(mtcars) #Displays structure
q <- ggplot(mtcars, aes(y= mpg, x= hp)) + #Creates plot
  xlab("HP") +
  ylab("MPG") + #Names
  ggtitle("HP vs MPG") +
  facet_grid(.~ cyl) + #Facet for cylinders
  facet_grid(.~ gear) #Facet for gears
q + geom_point() #Creates scatterplot
```

## Problem 3
*Using the `batting` data set (UsingR), create a visualization that does the following:*

* *Plots the* rate *of intentional walks (that is, the number of intentional walks divided by the number of times a player was at bat; these are the `IBB` and `AB` variables in the data set, respectively) against the* rate *of home runs (the `HR` variable in the data set) as a scatterplot*

* *Draws a trend line for these variables*

* *Identifies the outlier in the data set in these variables (spotted once the scatter plot is drawn)*


```{r, tidy = TRUE, error=TRUE}
str(batting) #Displays structure
q <- ggplot(batting, aes(x = (batting$IBB/batting$AB), y = (batting$HR/batting$AB))) +
     xlab("Rate of intentional walks") +
     ylab("Rate of home runs") +
     stat_smooth(method = "lm") #Creates line of best fit
q + geom_point() #Creates scatterplot of the two rates
#Outliers are identified by looking at the scatterplot (one around .17 and .12)
```

## BONUS Problem
*Reconsider the data set from a previous project containing data about the results of 2012 Olympics. I load the data in for you below:*

```{r}
# setwd("C:/Users/Deicy/Dropbox/Utah/MATH 3070 Fall 2018 - DJ/Lecture_7") #you will need to change to working directory to your own computer.
# olympic2012 <- read.csv("olympic-medals2012.csv")
# Some variables are read in as strings when, in truth, they are numeric (they separate thousands with commas, leading to them being read as strings). I fix this below using the transform function, which allows for modifying columns in a data frame using methods similar to with.
# olympic2012 <- transform(olympic2012, GDP.2011 = as.numeric(gsub(",", "", GDP.2011)), pop.2010 = as.numeric(gsub(",", "", pop.2010)))
```

*Use any plotting system (base R, **lattice**, **ggplot2**) to create plot involving at least three variables in the `olympic2012` data set. Explain the relationship you explored and any interesting findings. **Bonus points will be given for plots that I consider clean, clear, and insightful, accompanied with good analyses of what you found.***

```{r, tidy=TRUE, error=TRUE}
# Your code here
```