---
title: "MATH 3070 Lab Project 5"
author: "Kyle Kazemini"
date: "September 19, 2019"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***


## Problem 1
*Use the `subset()` function to return a data frame made from the `Cars93` (**MASS**) data frame consisting only of `non-USA` cars in origin, with 4 cylinders and a maximum price of \$15 or less.*

```{r, tidy=TRUE,error=TRUE}
library(MASS)
str(Cars93) #Shows structure of Cars93
subset(Cars93, subset = Cars93$Origin == "non-USA" && Cars93$EngineSize == 4 && Cars93$Max.Price <= 15)
#Creates subset with specified conditions
```

## Problem 2
*Find the standard deviation of each variable in the `mtcars` data set.*

```{r, tidy=TRUE, error=TRUE}
data("mtcars")
 #Square root of variance is standard deviation
sqrt(var(mtcars$mpg)) #Calculates standard deviation of mpg variable
sqrt(var(mtcars$cyl)) #Same calculation for the rest of the variables in the data set
sqrt(var(mtcars$disp))
sqrt(var(mtcars$hp))
sqrt(var(mtcars$drat))
sqrt(var(mtcars$wt))
sqrt(var(mtcars$qsec))
sqrt(var(mtcars$vs))
sqrt(var(mtcars$am))
sqrt(var(mtcars$gear))
sqrt(var(mtcars$carb))
```

## Problem 3
*Find the standard deviation for each numeric variable in `Cars93` (**MASS**).*

```{r, tidy=TRUE, error=TRUE}
#The variables in the calculations exclude non-numeric variables
str(Cars93) #This helps us determine which variables we want to use
sqrt(var(Cars93$Min.Price)) #Calculates standard deviation of the price variable
sqrt(var(Cars93$Price)) #Same calculation for the remaining numeric variables in Cars93
sqrt(var(Cars93$Max.Price))
sqrt(var(Cars93$MPG.city))
sqrt(var(Cars93$MPG.highway))
sqrt(var(Cars93$EngineSize))
sqrt(var(Cars93$Horsepower))
sqrt(var(Cars93$RPM))
sqrt(var(Cars93$Rev.per.mile))
sqrt(var(Cars93$Fuel.tank.capacity))
sqrt(var(Cars93$Passengers))
sqrt(var(Cars93$Length))
sqrt(var(Cars93$Wheelbase))
sqrt(var(Cars93$Width))
sqrt(var(Cars93$Turn.circle))
sqrt(var(Cars93$Rear.seat.room))
sqrt(var(Cars93$Luggage.room))
sqrt(var(Cars93$Weight))
```

## Problem 4
*You can find data describing various statistics on 2012 Olympic participating nations such as population and medal counts in the comma-separated value file (olympic-medals2012.csv). Load this dataset into R in a data frame and do the following:*

1. *Create a new data frame containing only the country's ISO code (a three-letter code for the country; USA is the United States of America, and DZA Algeria), name, population, and counts for gold, silver, and bronze. This data frame should be called `olympic2012`.*

```{r, tidy=TRUE, error=TRUE}
setwd("/Users/kylekazemini/Downloads")
olympic2012 <- read.csv("olympic-medals2012.csv") #The first two lines load the file into R
subset(olympic2012, subset = ISO == "USA" | ISO == "DZA", select = c("Country.name","pop.2010","Gold","Silver","Bronze")) #Creates subset with specified conditions
```

2. *What proportion of countries earned no medals? Answer this using `olympic2012`.*

```{r, tidy=TRUE, error=TRUE}
#Finds number with zero medals and divides it by total number of countries
length(which(olympic2012$Total.medal.score..gold.3..silver..2..bronze.1. == 0))/
length(olympic2012$Total.medal.score..gold.3..silver..2..bronze.1.)
```

