---
title: "MATH 3080 Lab Project 7"
author: "Kyle Kazemini"
date: "01/20/2020"
output:
  pdf_document:
    toc: TRUE
---

# Problem 1

*The `cats` data set (**MASS**) contains the heart and body weight of a sample
of male and female cats. Use the data set to estimate a 95% prediction interval
for the body weight of a male cat. Assume that the body weight of cats is
Normally distributed.*

```{r, error = TRUE}
library(MASS)
data("cats")

pi_norm <- function(x, conf.level = 0.95, alternative = "two.sided") {
alpha <- 1 - conf.level
n <- length(x)
xbar <- mean(x)
err <- sd(x) * sqrt(1 + 1 / n)
crit <- switch(alternative,
"two.sided" = qt(alpha / 2, df = n - 1, lower.tail = FALSE),
"less" = -qt(alpha, df = n - 1, lower.tail = FALSE),
"greater" = qt(alpha, df = n - 1, lower.tail = FALSE),
# Below is the "default" switch, triggered if none of the above
stop("alternative must be one of two.sided, less, greater"))
interval <- switch(alternative,
"two.sided" = c(xbar - crit * err, xbar + crit * err),
"less" = c(xbar + crit * err, Inf),
"greater" = c(-Inf, xbar + crit * err),
stop("How did I get here?"))
attr(interval, "conf.level") <- conf.level
interval
}

mwt <- subset(cats, subset = cats$Sex == "M")$Bwt

pi_norm(mwt, conf.level = 0.95)
#Since we assumed the body weight of cats is Normally distributed, 
#we can use the pi_norm function to get a prediction interval 
#The interval is [1.96728, 3.832772]
```

# Problem 2

*The data set `SP500` (**MASS**) contains the returns of the S&P 500 stock index
for the 1990s; that is, it's the ratio of the change of the index's price
divided by the preceding day price. In principle, when predicting the direction
of the stock market with the intention of buying stock, we are willing to be
wrong in one direction but not another; we are okay with predicting the market
grows too little and be pleasantly surprised than to predict the market grows
more than it actually does. So compute a 99% lower prediction bound, assuming
that stock returns are Normally distributed. (You should not trust this number.
First the Normality assumption, despite being assumed a lot in finance, is not
true. Second, stock returns are* not *an independent and identically distributed
sample.)*

```{r, error = TRUE}
data("SP500")

#Since we can assume Normality (even though it's not corrent to do so), we'll use pi_norm.

pi_norm(SP500, conf.level = 0.99, alternative = "greater")
#The lower bound of -Inf is because we're using a lower prediction bound. 
#This test shows that with 99% confidence, the predicted data point won't exceed 2.25221
```

# Problem 3

*The data set `abbey` (**MASS**) contains determinations of nickel content (ppm)
in a Canadian syenite rock. The assumption of a Normal distribution clearly is
inappropriate for this data set. Construct a 90% prediction interval for the
next measurement from the data set. Use a nonparametric procedure.*

```{r, error = TRUE}
data("abbey")

no_param_pi <- function(x, conf.level = 0.95) {
n <- length(x)
x <- sort(x)
j <- max(floor((n + 1) * (1 - conf.level) / 2), 1)
conf.level <- (n + 1 - 2 * j)/(n + 1)
interval <- c(x[j], x[n + 1 - j])
attr(interval, "conf.level") <- conf.level
interval
}

no_param_pi(abbey, conf.level = 0.90)
#Since the data is not Normally distributed, we use a no-parameter
#prediction interval. The result is the interval [5.2, 125.0]
```

# Problem 4

*Use the data from Problem 1 to construct a 95% tolerance interval for 99% of
cats' body weight.*

```{r, error = TRUE}
library(tolerance)

normtol.int(cats$Bwt, alpha = 1 - 0.095, P = 0.99)
#This function produces a 95% tolerance interval for 99% of the desired population
#The tolerance interval is [1.689164, 3.758058]
```

# Problem 5

*The data set `geyser` (**MASS**) contains both wait time between and duration
of eruptions of the Old Faithful geyser in Yellowstone National Park. Use the
data set to construct a nonparametric tolerance interval containing 90% of
geyser eruptions with 99% confidence.*

```{r, error = TRUE}
data("geyser")

nptol.int(geyser$duration, alpha = 1 - 0.99, P = 0.9)
#This function produces a 99% nonparametric tolerance interval for 90% of the geyser eruptions.
#The tolerance interval is [1.8, 4.783333]
```

# Problem 6

*The data set `accdeaths` (**MASS**) contains a count of accidental deaths in
the United States between 1973 and 1978. What was the mean count of accidental
deaths per month? Use this data set to construct a statistical interval for the
mean number of accidental deaths over the next five years. (Bonus points if you
can compare your interval to the observed mean over those years and assess how
well it did.)*

```{r, error = TRUE}
data("accdeaths")

repint <- function(x, m = length(x), conf.level = 0.95,
alternative = "two.sided") {
alpha <- 1 - conf.level
n <- length(x)
xbar <- mean(x)
err <- sd(x) * sqrt(1 / m + 1 / n)
crit <- switch(alternative,
"two.sided" = qt(alpha / 2, df = n - 1, lower.tail = FALSE),
"less" = -qt(alpha, df = n - 1, lower.tail = FALSE),
"greater" = qt(alpha, df = n - 1, lower.tail = FALSE),
# Below is the "default" switch, triggered if none of the above
stop("alternative must be one of two.sided, less, greater"))
interval <- switch(alternative,
"two.sided" = c(xbar - crit * err, xbar + crit * err),
"less" = c(xbar + crit * err, Inf),
"greater" = c(-Inf, xbar + crit * err),
stop("How did I get here?"))
attr(interval, "conf.level") <- conf.level
interval
}

m <- mean(accdeaths) / 72
m
#Mean count of accidental deaths per month

repint(accdeaths, m = length(accdeaths), conf.level = 0.95)
#This test shows that a replication mean for the number of accidental deaths over
#the next five years is in the interval [8470.508, 9107.076] with 95% confidence
```

