---
title: "MATH 3080 Lab Project 10"
author: "Kyle Kazemini"
date: "02/05/2020"
output:
  pdf_document:
    toc: TRUE
---

# Problem 1 (Verzani problem 11.22)

*For the data set `trees`, model the `Volume` by the `Girth` and `Height`
variables. Does the model fit the data well?*

```{r, error = TRUE}
data("trees")

fit <- lm(Volume ~ Girth + Height, data = trees)
#This models the volume based on multiple variables

summary(fit)$r.squared
#This R squared value shows that the model fits the data well
```

# Problem 2 (Verzani problem 11.24)

*For the `deflection` (**UsingR**) data set, fit the quadratic model*

$$\text{Deflection} = \beta_0 + \beta_1 \text{Load} + \beta_2 \text{Load}^2 +
\epsilon.$$

*How well does this model fit the data? Compare to the linear model.*

```{r, error = TRUE}
data("deflection")

fit <- lm(Deflection ~ Load + I(Load^2), data = deflection)

summary(fit)$r.squared
#This is an excellent model for the data

linear <- lm(Deflection ~ Load, data = deflection)

summary(linear)$r.squared
#This is also an excellent model for the data
```

# Problem 3 (Verzani problem 11.25)

*The data set `kid.weights` contains age, weight, and height measurements for
several children. Fit the linear model*

$$\text{weight} = \beta_0 + \beta_1 \text{age} + \beta_2 \text{height} + \beta_3
\text{height}^2 + \beta_4 \text{height}^3 + \beta_5 \text{height}^4$$

*Use the partial $F$-test to select between this model and the nested models
found by using only first-, second-, and third-degree polynomials for `height`.*

```{r, error = TRUE}
data("kid.weights")

fit <- lm(weight ~ age + height, data = kid.weights)

fit2 <- lm(weight ~ height, data = kid.weights)
fit3 <- lm(weight ~ height + I(height^2), data = kid.weights)
fit4 <- lm(weight ~ height + I(height^2) + I(height^3), data = kid.weights)

anova(fit, fit2, fit3, fit4)
#This test shows that model 4 is the best
```

# Problem 4 (Verzani problem 11.27)

*The data set `Cars93` (**MASS**) contains data on cars sold in the United
States in the year 1993. Fit a regression model with `MPG.city` modeled by the
numeric variables `EngineSize`, `Weight`, `Passengers`, and `Price`. Which
variables are marked as statistically significant by the marginal $t$-tests?
Which model is selected by the AIC?*

```{r, error = TRUE}
data("Cars93")

aic_compare <- function(fit1, fit2) {
  exp((AIC(fit1) - AIC(fit2)) / 2)
}

min_aic_model <- function(...) {
  models <- list(...)
  aic_list <- sapply(models, AIC)
  best_model <- models[[which.min(aic_list)]]
  best_model
}

fit <- lm(MPG.city ~ EngineSize, data = Cars93)
fit2 <- lm(MPG.city ~ Weight, data = Cars93)
fit3 <- lm(MPG.city ~ Passengers, data = Cars93)
fit4 <- lm(MPG.city ~ Price, data = Cars93)

best_fit <- min_aic_model(fit, fit2, fit3, fit4)

sapply(list(fit, fit2, fit3, fit4), function(l) {aic_compare(best_fit, l)})
#This shows that the best model is fit3
```

# Problem 5 (Verzani problem 11.29)

*The data set `baycheck` (**UsingR**) contains estimated populations for a
variety of Bay Checkerspot butterflies near California. A common model for
population dynamics is the Ricker model, for which $t$ is time in years:

$$N_{t + 1} = aN_t e^{bN_t} W_t,$$

*where $a$ and $b$ are parameters and $W_t$ is a lognormal multiplicative error.
This can be turned into a regression model by dividing by $N_t$ and then taking
logs of both sides to give*

$$\log\left(\frac{N_{t + 1}}{N_t}\right) = \log(a) + b N_t + \epsilon_t.$$

*Let $y_t$ be the left-hand side. This may be written as*

$$y_t = r\left(1 - \frac{N_t}{K}\right) + \epsilon_t,$$

*because $r$ can be interpreted as an unconstrained growth rate and $K$ as a
carrying capacity.*

*Fit the model to the `baycheck` data set and find values for $r$ and $K$. To
find $y_t$ you can do the following:*

```{r, error = TRUE}
d <- with(baycheck, {
  n <- length(year)
  yt <- log(Nt[-1]/Nt[-n])
  nt <- Nt[-n]
  data.frame(yt, nt)
})
```

*Recall that a negative index means all but that index.*

```{r, error = TRUE}
fit <- lm(d$nt ~ d$yt, data = baycheck)
fit
#This is a simple model based on the calculations and formulas above
```

