---
title: "MATH 3080 Lab Project 3"
author: "Kyle Kazemini"
date: "12/29/2019"
output:
  pdf_document:
    toc: TRUE
---

# Problem 1

*List all the S3 methods associated with the `summary()` generic function.*

```{r, error = TRUE}
methods(summary)
#This displays all S3 methods of summary.
```

# Problem 2

*There is no function in the **stats** package for the $z$ test. In this
exercise, you will write that function. Furthermore, since we want this function
to emulate functions such as `t.test()`, you will write a function `z.test()`
that returns an `htest`-class object. This is mostly so we can take advantage of
`print.htest()` in the **stats** package:*

```{r}
stats:::print.htest
```

*Let's start by studying the structure of the object returned by `t.test()`:*

```{r}
x <- rnorm(10)
res <- t.test(x)
str(res)
```

*Let's also look at the `t.test()` function. It turns out that `t.test()` is a
generic function, so we should actually look at `t.test.default()`:*

```{r}
args(stats:::t.test.default)
```

*Based on this we should have our `z.test()` function take the following
inputs:*

* *`x`: The input data vector*
* *`sigma`: The value of the population standard deviation*
* *`mu`: The population mean under the null hypothesis*
* *`alternative`: A string that's one of `"two.sided"`, `"less"`, or
  `"greater"`, which matters for both the null hypothesis and the confidence
  interval returned*
* *`conf.level`: A number representing the confidence level of the confidence
  interval*

*The output of `z.test()` should resemble `res` shown above.*

```{r, error = TRUE}
z.test <- function(x, sigma = NULL, mu = 0, alternative = "two.sided",
                   conf.level = 0.95) {
  rval <- list()

  # I will do this part: understanding the following line requires
  # metaprogramming knowledge
  rval$data.name <- deparse(substitute(x))
  
  if (is.null(sigma)) {
    sigma <- sd(x)
  }

  xbar <- mean(x)
  n <- length(x)
  z<- (xbar - mu) / (sigma / sqrt(n))
  stderr <- sigma / sqrt(n)
  estimate <- mean(x)
  conf.int <- confint(x, sigma, level = 0.95)
  null.value <- NULL
  alternative <- "two.sided"
  method <- "z.test"
  
  rval$statistic <- c(statistic = z)
  rval$parameter <- c(sigma = sigma)  # I'll also do parameter
  rval$conf.int <- c(conf.int = conf.int)
  rval$estimate <- c(estimate = estimate)
  rval$null.value <- c(null.value = null.value)
  rval$stderr <- c(stderr = stderr)
  rval$alternative <- c(alternative = alternative)
  rval$method <- c(method = method)
  
  class(rval) <- "htest"
  return(str(rval))
}
```

*The code below tests that `z.test()` works as intended.*

```{r, error = TRUE}
# Test code: DO NOT EDIT!
dat <- c(0.6, -0.7, 0.8, -0.2, 1.8, 0.1, 0.1, -0.4, -0.6, 0.6)
z.test(dat, sigma = 1)
z.test(dat, sigma = 2, mu = 1, alternative = "less", conf.level = 0.9)
z.test(dat, sigma = 0.5, mu = 2, alternative = "greater", conf.level = 0.99)
```

# Problem 3

*Design S3 classes representing:*

* *A circle*
* *A rectangle*
* *A square*

*Be sure to write functions that construct these objects for the user. Then
write two generic functions, `area()` and `perimeter()`, that find the area and
perimeters of the respective objects. Write `print()` methods for your objects.
Demonstrate that your code works. These objects should be defined in meaningful
ways, allowing users to create objects of different size and shape.*

**BONUS:** *Since squares are also rectangles, you could save time and write
better code by having the square class inherit from the rectangle class. You
should have separate `print()` methods for squares and rectangles, but the
`area()` and `perimeter()` methods could be shared.*

```{r, error = TRUE}
rectangle <- function(width, height){
  w <- c(width = width, height = height)
  class(w) <- "rectangle"
  w
}
circle <- function(radius){
  r <- c(radius = radius)
  class(r) <- "circle"
  r
}

square <- function(sideLength){
  s <- c(sideLength = sideLength)
  class(s) <- c("square", "rectangle")
  s
}

perimiter <- function(x) usedMethod("perimiter")

perimiter.rectangle <- function(x){
  (x[{"width"}]*2) + (x[{"height"}]*2)
}

area.rectangle <- function(width, height){
  (x[{"width"}]) * (x[{"height"}])
}

perimiter.circle <- function(radius){
  (x[("radius")]*2*pi)
}

area.circle <- function(radius){
 (x[("radius")]^2*pi)
}

print.circle <- function(x) {
  cat("Circle of radius", x[["radius"]], "\n")
}

print.rectangle <- function(x){
  cat("Rectangle with width", x[["width"]], "and height", x[["height"]], "\n")
}

print.square <- function(x){
  cat("Square with side length ", x[["sideLength"]], "\n")
}

circle(3)
rectangle(4, 5)
square(4)
circle(12)
```

