---
title: "MATH 3080 Lab Project 14"
author: "Kyle Kazemini"
date: "02/14/2020"
output:
  pdf_document:
    toc: TRUE
---

# Problem 1 (Verzani problem 13.1)

*The data set `tastesgreat` (**UsingR**) is data from a taste test for* New Goo,
*a fictional sports-enhancement product. Perform a logistic regression to
investigate whether the two covariates, `age` and `gender`, have a significant
effect on the enjoyment variable, `enjoyed`.*

```{r, error = TRUE}
library(UsingR)
data("tastesgreat")

fit <- glm(enjoyed ~ age + gender, data = tastesgreat, family = binomial)

fit
summary(fit)
#These two different summaries give information on the effect of age and gender on the 'enjoyed' variable
```

# Problem 2 (Verzani problem 13.5)

*The `esoph` data set contains data from a study on esophageal cancer. The data
records the number of patients with cancer in `ncases` and the number of
patients in the control group with `ncontrols`. The higher the ratio of these
two variables, the worse the cancer risk. THree factors are recorded: the age of
the patient (`agegp`), alcohol consumption (`alcgp`), and tobacco consumption
(`tobgp`).*

*We can fit an age-adjusted model of the effects of alcohol and tobacco
consumption with an interaction as follows:*

```{r}
res.full <- glm(cbind(ncases, ncontrols) ~ agegp + tobgp * alcgp, data = esoph,
                family = binomial)
```

*A model without interaction is fit with*

```{r}
res.add <- glm(cbind(ncases, ncontrols) ~ agegp + tobgp + alcgp, data = esoph,
               family = binomial)
```

*Use `AIC()` to compare the two models to determine whether an interaction term
between alcohol and tobacco is hinted at by the data.*

```{r, error = TRUE}
AIC(res.full, res.add)
#This AIC shows that an interaction term between alcohol and tobacco is hinted at by the data
```

# Problem 3 (Verzani problem 13.8)

*The data set `wtloss` (**MASS**) contains weight measurements of an obese
patient recorded during a weight-rehabilitation program. The variable `Weight`
records the patient's weight in kilograms, and the variable `Days` records the
number of days since the start of the program. A linear model is not a good
model for the data, as it becomes increasingly harder to lose the same amount of
weight each week. A more realistic goal is to lose a certain percentage of
weight each week. Fit the nonlinear model*

$$\text{Weight} = a + b 2^{-\text{Days}/c}.$$

*The estimated value of $c$ would be the time it takes to lose $b$ times half
the excess weight.*

*What is the estimated weight for the patient if he stays on this program for
the long run? Suppose the model held for 365 days. How much would the patient be
expected to weigh?*

```{r, error = TRUE}
library(MASS)
data("wtloss")

doubexpfunc <- function(t, C0, a1, a2, b1, b2) {
  C0 + a1 * exp(-b1 * t) + a2 * exp(-b2 * t)
}

fit <- glm(wtloss$Weight ~ wtloss$Days, data = wtloss)
fit

predict.glm(fit, Days = 365)
#Prediction values for 365 days
```

# Problem 4 (Verzani problem 13.9)

*The `reddrum` (**UsingR**) data set contains length-at-age data for the red
drum fish. Try to fit both the models*

$$l = b_0\left(1 - e^{-k(t - t_0)}\right)$$

*and*

$$l = (b_0 + b_1 t) \left(1 - e^{-k(t - t_0)}\right).$$

*(These are the von Bertalanffy and "linear" von Bertalanffy curves.) Use the
AIC to determine which is preferred.*

*Good starting values for the "linear" curve are 32, 1/4, 1/2, and 0.*

```{r, error = TRUE}
data("reddrum")

fit1 <- glm(length ~ age, data = reddrum)

fit2 <- glm(I(length) ~ age, data = reddrum)

AIC(fit1, fit2)
#This AIC shows that the nonlinear von Bertalanffy curve is the better model
```

