---
title: "MATH 3080 Lab Project 12"
author: "Kyle Kazemini"
date: "02/05/2020"
output:
  pdf_document:
    toc: TRUE
---

# Problem 1 (Verzani problem 9.17)

*The `exec.pay` (**UsingR**) data set contains data on the salaries of CEOs at
199 top companies in the United States. The amounts are in \$10,000s. The data
is not symmetric. Do a sign test to determine whether the median pay is more
than \$220,000.*

```{r, error = TRUE}
library(UsingR)
data("exec.pay")

sign.test <- function(x, q = 0, p = 0.5, alternative = "two.sided") {
res <- list()
res$data.name <- deparse(substitute(x))
res$estimate <- c("quantile" = quantile(x, p)[[1]])
x <- x[x != q] # Delete observations matching q exactly
res$method <- "Sign Test"
res$parameter <- c("p" = p)
res$alternative <- alternative
res$null.value <- c("quantile" = q)
res$statistic <- c("T" = sum(x > q))
n <- length(x)
res$p.value <- with(res, switch(alternative,
greater = pbinom(statistic - 1, size = n, prob = p, lower.tail = FALSE),
less = pbinom(n - statistic + 1, size = n, prob = p, lower.tail = FALSE),
two.sided = pbinom(max(statistic - 1, n - statistic + 1), size = n,
prob = p, lower.tail = FALSE)
))
class(res) <- "htest"
res
}

sign.test(exec.pay, q = 220000, p = 0.5, alternative = "greater")
#This p-value suggests that the median pay is not more than $220,000
```

# Problem 2 (Verzani problem 9.18)

*Repeat the previous exercise, using the signed-rank test on the log-transformed
data. Do you reach the same conclusion?*

```{r, error = TRUE}
log <- log1p(exec.pay)
sign.test(log, q = 220000, p = 0.5, alternative = "greater")
#The same conclusion is reached from the log-transformed data. 
#The median pay is not more than $220,000
```

# Problem 3 (Verzani problem 9.20)

*If the sign test has fewer assumptions on the population, why wouldn't we
always use that instead of a $t$-test? The answer lies in the power of the sign
test to detect when the null hypothesis is false. The sign test will not reject
a false null as often as the $t$-test. The following commands will perform a
simulation comparing the two tests on data that has a $N(1, 2)$ distribution.
The significance tests performed are both*

$$H_0: \mu = 0$$

$$H_A: \mu > 0.$$

*Run the simulation. Is there a big difference between the two tests?*

```{r}
m <- 200; n <- 10

out <- replicate(m, {
  x <- rnorm(n, mean = 1, sd = 2)
  ttest <- t.test(x, mu = 0, alt = "greater")$p.value
  sgntest <- 1 - pbinom(sum(x > 0) - 1, n, 1/2)
  c(t.test = ifelse(ttest < 0.05, 1, 0),
    sign.test = ifelse(sgntest < 0.05, 1, 0))
})

res.t <- out["t.test",]
res.sign <- out["sign.test",]
results <- c(t = sum(res.t)/m, sign = sum(res.sign) / m)
results
```

There is a significant difference between the two tests. This is because the sign test shows 
less evidence of successes (ie the median is exceeded). This is because the sign test is 
basically a test for population proportion.

# Problem 4 (Verzani problem 9.31)

*For the `babies` (**UsingR**) data set, the variable `age` contains the
recorded mom's age and `dage` contains the dad's age for several different cases
in the sample. Do a significance test of the null hypothesis of equal ages
against a one-sided alternative that the dads are older in the sampled
population.*

```{r, error = TRUE}
data("babies")

mom <- babies$age
dad <- babies$dage

wilcox.test(mom, dad, alternative = "greater")
#There is not sufficient evidence to show that the dads are older in the sample population
```

# Problem 5 (Verzani problem 9.32)

*The data set `normtemp` (**UsingR**) contains body measurements for 130
healthy, randomly selected individuals from some parent population. The variable
`temperature` contains normal body temperature data and the variable `gender`
contains gender information, with male coded as 1 and female as 2. Is the sample
difference across the two groups statistically significant?*

```{r, error = TRUE}
data("normtemp")

temp <- normtemp$temperature
gender <- normtemp$gender

wilcox.test(temp, gender, alternative = "greater")
#There is sufficient evidence to show a difference across the two groups
```

