---
title: "MATH 3080 Lab Project 4"
author: "Kyle Kazemini"
date: "12/29/2019"
output:
  pdf_document:
    toc: TRUE
---

# Problem 1 (Verzani problem 12.2)

*For the data set `Cars93` (**MASS**) perform a one-way analysis of variance of
`MPG.highway` for each level of `DriveTrain`. Does the data support the null
hypothesis of equal population means? (Use `aov()` for this problem.)*

```{r, error = TRUE}
library(MASS)
data(Cars93)

res <- aov(MPG.highway ~ DriveTrain, data = Cars93)
print(res)
summary(res)
#This data does support the null hypothesis of equal population means.
```

# Problem 2 (Verzani problem 12.4)

*The data set `carsafety` (**UsingR**) contains car-crash data. For several
makes of cars the number of drivers killed per million is recorded in
`Drivers.deaths`. The number of drivers of other cars killed in accidents with
these cars, per million, is recorded in `Other.deaths`. The variable `type` is a
factor indicating the type of car.*

*Perform a one-way analysis of variance of the model `Drivers.deaths ~ type`. Is
there a difference in population means? Did you assume equal variances? Normally
distributed populations?*

*Repeat with an analysis of variance of the model `Other.deaths ~ type`. Is
there a difference in population means? (Use `oneway.test()` for this problem.)*

```{r, error = TRUE}
library(UsingR)
data(carsafety)

res1 <- oneway.test(Driver.deaths ~ type, data = carsafety)
print(res1)
summary(res1)
#This test shows that there's no difference in population means. 
#We assumed equal variances and normally distributed populations.

res2 <- oneway.test(Other.deaths ~ type, data = carsafety)
print(res2)
summary(res2)
#This test shows that there is a non-trivial difference in population means.
#We assumed equal variances and normally distributed populations.
```

# Problem 3 (Verzani problem 12.7)

*A manufacturer of point-of-sale merchandise tests three types of ENTER-button
markings. They wish to minimize wear, as customers get annoyed when the markings
on this button wear off. They construct a test of the three types, and conduct
several trials for each. The results, in unspecified units, are recorded in the
following table:*

|        |     |     |     |     |     |     |
|--------|-----|-----|-----|-----|-----|-----|
| Type 1 | 303 | 293 | 296 | 299 | 298 |     |
| Type 2 | 322 | 326 | 315 | 318 | 320 | 320 |
| Type 3 | 309 | 327 | 317 | 315 |     |     |

*Is there a difference in wear time among the three types? Answer this using a
one-way ANOVA.*

```{r, error = TRUE}
df <- data.table::data.table(c("Type 1" = 303, 293, 296, 299, 298), c("Type 2" = 322, 326, 315, 318, 320, 320), 
                             c("Type 3" = 309, 327, 317, 315))

res1 <- aov(V1 ~ V2, data = df)
print(res1)

res2 <- aov(V1 ~ V3, data = df)
print(res2)

res3 <- aov(V2 ~ V3, data = df)
print(res3)

#Based on the results from the ANOVA tests, there is a difference in wear time among the three types.
```

# Problem 4 (Verzani problem 12.13)

*For the data in Problem 2, perform the one-way ANOVA using `lm()`. Compare to
the results of `oneway.test()`.*

```{r, error = TRUE}
res1 <- lm(Driver.deaths ~ type - 1, data = carsafety)
print(res1)
summary(res1)

res2 <- lm(Other.deaths ~ type - 1, data = carsafety)
print(res2)
summary(res2)

#The results are different for both of the above tests from the tests in problem two
#because the lm function gives more classes and values for the data.
```

# Problem 5 (Verzani problem 12.19)

*The `InsectSprays` data set contains a variable `count`, which counts the
number of insects and a factor `spray`, which indicates the treatment given.*

*First perform an analysis of variance to see whether the treatments make a
difference. If so, perform the Tukey HSD procedure to see which pairwise
treatments differ.*

```{r, error = TRUE}
data("InsectSprays")

res <- aov(count ~ spray, data = InsectSprays)
print(res)
#The aov test indicates that the treatment makes a difference.

TukeyHSD(res)
plot(TukeyHSD(res))
#This plot shows the differences in pairwise treatments.
#Zero is in several of these intervals. This means there's significant evidence
#that some pairs have the same means and some don't.
```

