---
title: "MATH 3080 Lab Project 13"
author: "Kyle Kazemini"
date: "02/11/2020"
output:
  pdf_document:
    toc: TRUE
---

# Problem 1 (Verzani problem 10.1)

*A die is rolled 100 times and yields these frequencies*

|       |  1 |  2 | 3 |  4 |  5 |  6 |
|-------|----|----|---|----|----|----|
| count | 13 | 17 | 9 | 17 | 18 | 26 |

*Is this a fair die? Answer using a significance test with $H_0: p_i =
\frac{1}{6}$ for each $i$, and $H_A: p_i \neq \frac{1}{6}$ for at least one
$i$.*

```{r, error = TRUE}
pos <- c(1, 2, 3, 4, 5, 6)
count <- c(13, 17, 9, 17, 18, 26)

chisq.test(pos, count)
#This is a goodness of fit test. The p-value means the null hypothesis was not rejected
```

# Problem 2 (Verzani problem 10.5)

*A simple trick for determining what language a document is written in is to
compare the letter distributions (e.g., the number of z's) to the known
proportions for a language. For these proportions, we use the familiar letter
frequencies given in the `frequencies` variable of the `scrabble` (**UsingR**)
data set. These are an okay approximation to those in the English language.*

*For simplicity (see `?scrabble` for more details), we focus on the vowel
distribution of a paragraph from R's webpage appearing below. The counts and
Scrabble frequencies are given in the table below.*

|                    |  a |  e |  i |  o |  u |
|--------------------|----|----|----|----|----|
| Count              | 28 | 39 | 23 | 22 | 11 |
| Scrabble frequency |  9 | 12 |  9 |  8 |  4 |

> R is a language and environment for statistical computing and graphics. It is
> a GNU project which is similar to the S language and environment which was
> developed at Bell Laboratories (formerly AT&T, now Lucent Technologies) by
> John Chambers and colleagues. R can be considered as a different
> implementation of S. There are some important differences, but much code
> written for S runs unaltered under R.

*Perform a chi-squared goodness-of-fit test to see whether the distribution of
vowels appears to be from English.*

```{r, error = TRUE}
count <- c(28, 39, 23, 22, 11)
frequency <- c(9, 12, 9, 8, 4)

chisq.test(count, frequency)
#The p-value means that we reject the null hypothesis 
#and the distribution of vowels appears to be from English
```

# Problem 3 (Verzani problem 10.6)

*The names of common stars are typically Greek or Arab in derivation. The
`bright.stars` (**UsingR**) data set contains 96 names of common stars. Perform
a significance test on the letter distribution to see whether they could be
mistaken for English words.*

*The letter distribution can be found with:*

```{r, error = TRUE}
library(UsingR)
all.names <- paste(bright.stars$name, sep = "", collapse = "")
x <- unlist(strsplit(tolower(all.names), ""))
letter.dist <- sapply(letters, function(i) sum(x == i))
```

*The English-letter frequency is found using the `scrabble` (**UsingR**) data
set with:*

```{r}
ps <- scrabble$frequency[1:26]
ps <- ps / sum(ps)
```

```{r, error = TRUE}
chisq.test(ps, letter.dist)
#This is a significance test on the letter distribution
#The null hypothesis is rejected meaning they could be mistaken for English words
```

# Problem 4 (Verzani problem 10.12)

*The `airquality` data set contains measurements of air quality in New York
City. We wish to see if ozone levels are independent of temperature. First we
gather the data, using `complete.cases` to remove missing data from our data
set.*

```{r}
aq <- airquality[complete.cases(airquality),]
aq <- transform(aq,
  te = cut(Temp, quantile(Temp)),
  oz = cut(Ozone, quantile(Ozone))
)
xtabs(~ te + oz, data = aq)
```

*Perform a chi-squared test of independence on the two variables `te` and `oz`.
Does the data support an assumption of independence?*

```{r, error = TRUE}
chisq.test(aq$te, aq$oz)
#The null hypothesis is rejected and 
#the data supports an assumption of independence
```

# Problem 5 (Verzani problem 10.14)

*The data set `oral.lesion` (**UsingR**) contains data on location of an oral
lesion for three geographic locations. This data set appeared in an article by
Mehta and Patel about differences in $p$-values in tests for independence when
the exact or asymptotic distributions are used. Compare the $p$-values found by
`chisq.test()` when the asymptotic distribution of the sampling distribution is
used to find the $p$-value and when a simulated value is used. Are the
$p$-values similar? If not, which do you think is more accurate? Why?*

```{r, error = TRUE}
library(UsingR)
data("oral.lesion")

chisq.test(oral.lesion)
chisq.test(oral.lesion, simulate.p.value = TRUE, B = 10000)
#The p-values are fairly similar, but I think that the one from the asymptotic distribution are more accurate
#This could be because simulated p-values are less accurate
```

